%% Date Created: December 3, 2024
%% Last Modified: December 3, 2024
%% Template Available on GitHub at: https://github.com/elcarrillo/academic_cv_latex

\documentclass[a4paper,10pt]{article}
% Package imports for layout, fonts, icons, colors, etc.
\usepackage[margin=2cm]{geometry} % Page layout
\usepackage{titlesec}             % Custom section titles
\usepackage{setspace}             % Line spacing
\usepackage{enumitem}             % Custom list formats
\usepackage{xcolor}               % Custom colors
\usepackage{fancyhdr}             % Custom headers/footers
\usepackage{hyperref}             % Clickable URLs and links
\usepackage{fontawesome}          % Social media icons (GitHub, email)
\usepackage{tabularx}             % Responsive tables
\usepackage{hanging}              % Hanging indents for citations
\usepackage{helvet}               % Sans-serif font (Helvetica)
\usepackage{datetime}             % Custom date/time

% Redefine \today to show only month and year
\renewcommand{\today}{\monthname[\the\month] \the\year}

\renewcommand{\familydefault}{\sfdefault} % Set default font to sans-serif
\definecolor{Black}{RGB}{0,0,128}      % Custom colors

% Title formatting for sections
\titleformat{\section}  
  {\color{black}\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}] 
\titleformat{\subsection}  
  {\normalfont\bfseries}{\thesubsection}{1em}{\underline}[]
\titleformat{\subsubsection}  
  {\normalfont\bfseries\itshape}{\thesubsubsection}{1em}{}[{}]

\titlespacing*{\subsubsection}{0pt}{0ex}{0ex}

% Line spacing
\setstretch{1.2}

% Footer
\pagestyle{fancy}  % Set the general footer for all pages
\fancyhf{}         % Clear all header and footer fields

%% Define footer for all pages 
\renewcommand{\headrulewidth}{0pt}  % Remove the line at the top
\fancyfoot[L]{Your Name}            % Left-aligned name
\fancyfoot[C]{\thepage}             % Center-aligned page number
\fancyfoot[R]{\today}               % Right-aligned date

% Custom footer for the first page
\fancypagestyle{firstpagefooter}{
    \fancyhf{}  % Clear header and footer on the first page
    % \fancyfoot[L]{Custom text for the first page}  % Custom left footer text
    \fancyfoot[C]{\thepage}  % Custom center footer text
    \fancyfoot[R]{\today}    % Custom right footer text
}
%% To use, insert the following command after title text: \thispagestyle{firstpagefooter} 

% Custom hyperlink formatting 
\hypersetup{
    colorlinks=true,  % Keep links like URLs visible
    linkcolor=black,  % Link color
    urlcolor=blue,    % URLs color
    citecolor=black,  % Citation links colors
    linkbordercolor={1 1 1}, % Hides boxes around links (for page numbers)
}

%% Custom subheading - can be used in place of subsection heading 
\newcommand{\subheading}[1]{\vspace{0.5cm}\noindent\makebox[\textwidth][l]{\underline{\textbf{#1}}}\par\vspace{0.3cm}} 
    % Makebox controls overfull underlines

\raggedbottom %% Stops LaTeX from stretching content to fill the page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  Begin document                                                                              %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{\LARGE\bfseries Your Name}
\author{}
\date{}

\maketitle \vspace{-2.0cm} % Vspace -# gets rid of space from empty \author and \date

\begin{center}
    Ph.D. Candidate $\cdot$ Department of Biochemistry $\cdot$ University of Science \\
    
    \faEnvelope\ \href{mailto:email@example.com}{email@example.com} $\cdot$ 
    \faGlobe\ \href{https://yourwebsite.com}{yourwebsite.com} $\cdot$ 
    \faGithub\ \href{https://github.com/yourusername}{github.com/yourusername} 
    % \faLinkedin\ \href{https://linkedin.com/in/yourprofile}{linkedin.com/in/yourprofile}
\end{center}

%% Use custom footer on the first page
\thispagestyle{firstpagefooter}

\section*{Education}
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{2.5cm} X}
2020 -- Present & \textbf{University of Science}, City, State \\
                & Ph.D. in Biochemistry \\
                & Dissertation: \textit{[Title of Dissertation]} \\
                & Advisor: Dr. [Advisor's Name] \\
\\
2016 -- 2020    & \textbf{University of Knowledge}, City, State \\
                & Bachelor of Science in Biochemistry \\
                & Honors: Magna Cum Laude \\
\end{tabularx}

\section*{Research Interests}
Enzyme kinetics, protein engineering, metabolic pathway analysis, structural biology, and drug design.

\section*{Research Experience}
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{2.5cm} X}
2020 -- Present & \textbf{Graduate Research Assistant}, University of Science, Department of Biochemistry \\
                & \textit{Project Title:} Investigation of enzyme mechanisms in metabolic pathways \\
                & Responsibilities: Conducted experiments on enzyme kinetics, utilized X-ray crystallography for structural analysis, collaborated with computational chemists for drug design simulations. \\
\\
2018 -- 2020    & \textbf{Undergraduate Research Assistant}, University of Knowledge, Department of Chemistry \\
                & \textit{Project Title:} Synthesis of small molecule inhibitors for cancer therapy \\
                & Responsibilities: Performed organic synthesis of novel compounds, analyzed results using NMR and mass spectrometry, assisted in writing a publication draft. \\
\end{tabularx}

\section*{Publications}

\subsubsection*{Peer-Reviewed Articles}
\hangindent=1.5em \hangafter=1
\textbf{Your Last Name, First Initial.}, Co-author, Co-author. (Year). Title of the article. \textit{Journal Name}, \textit{Volume}(Issue), pages. \href{DOI or URL}{DOI or URL}

\hangindent=1.5em \hangafter=1
\noindent Co-author, \textbf{Your Last Name, First Initial.}, Co-author. (Year). Title of the article. \textit{Journal Name}, \textit{Volume}(Issue), pages. \href{DOI or URL}{DOI or URL}

\subsubsection*{Manuscripts in Preparation}
\hangindent=1.5em \hangafter=1
\textbf{Your Last Name, First Initial.}, Co-author. Title of the manuscript. Intended journal.

\section*{Conference Presentations}
\hangindent=1.5em \hangafter=1 
\textbf{Your Last Name, First Initial.}, Co-author. (Year, Month). Title of the presentation. Poster session presented at the Conference Name, City, State.

\hangindent=1.5em \hangafter=1 
\noindent Co-author, \textbf{Your Last Name, First Initial.} (Year, Month). Title of the presentation. Oral presentation at the Conference Name, City, State.

\section*{Teaching Experience}

\subsection*{University of Science, City, State}
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{2.5cm} X}
Fall 2023 & \textbf{Teaching Assistant}, Biochemistry I \\
          & Assisted in teaching undergraduate students fundamental concepts of biochemistry, held weekly office hours, and graded assignments and exams. \\
\\
Spring 2022 & \textbf{Laboratory Instructor}, Molecular Biology Lab \\
            & Supervised lab sessions, instructed students on lab techniques such as PCR and gel electrophoresis, ensured safety protocols were followed. \\
\end{tabularx}

\section*{Grants and Fellowships}
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{1.5cm} X}
2024 & \textbf{Graduate Research Fellowship}, National Science Foundation \\
2023 & \textbf{Travel Grant}, Biochemical Society \\
2021 & \textbf{Departmental Scholarship}, University of Science \\
\end{tabularx}

\section*{Honors and Awards}
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{1.5cm} X}
2020 & \textbf{Outstanding Undergraduate Researcher Award}, University of Knowledge \\
2019 & \textbf{Dean's List}, University of Knowledge (2017 -- 2020) \\
2018 & \textbf{Scholarship}, American Chemical Society \\
\end{tabularx}

\section*{Laboratory Skills}
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{5cm} X}
\textbf{Enzyme Kinetics Assays} & Proficient in designing and conducting enzyme kinetics experiments, including Michaelis-Menten and inhibition assays. \\
\textbf{Protein Purification and Characterization} & Experienced in chromatography techniques (HPLC, FPLC), SDS-PAGE, and Western blotting for protein analysis. \\
\textbf{Structural Biology Techniques} & Skilled in X-ray crystallography and cryo-electron microscopy for determining protein structures. \\
\textbf{Spectroscopic Methods} & Knowledgeable in mass spectrometry, NMR spectroscopy, UV-Vis, and fluorescence spectroscopy. \\

\textbf{Bioinformatics Tools} & Proficient in using BLAST, PyMOL, Chimera, and sequence alignment software for computational analysis. \\
\end{tabularx}

\section*{Professional Memberships}
American Society for Biochemistry and Molecular Biology (ASBMB), Biophysical Society, American Chemical Society (ACS)

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  End document                                                                                %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Section General Format:
%% ------------------------------------
% \section*{Section Title}
% \begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{2.5cm} X}
% Dates & \textbf{Position Title}, Organization, City, State \\
%       & Description of role or project.
% \end{tabularx}
%% ------------------------------------

%% Listing Publications
%% --------------------------------------------------------------------------------------------
%% Use a hanging indent to format citations.
%% Example:
% \hangindent=1.5em \hangafter=1
% \textbf{Your Last Name, First Initial.}, Co-author. (Year). Title of the article. \textit{Journal Name}, \textit{Volume}(Issue), pages.

%% --------------------------------------------------------------------------------------------
